UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-24 main.tex
:construction: Update figures

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution under different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each UniScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
	\end{subsection}

	\begin{subsection}{Backscatter Rate versus Output Discretization Bit}
		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we now investigate the impact of threshold domain discretization on the total backscatter rate.

@@

	\begin{subsection}{Rate Region of Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
				``BSP'' means backscatter symbol period.
			}
		\end{figure}
		For the \gls{bcd} algorithm considered in the rest of this paper, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
		The impacts of different schemes are explored below.

@@

	\begin{subsection}{Rate Region vs. System Configuration}
		\begin{figure}[!t]
			\centering
			\subfloat[Metscatter Nodes\label{fi:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fi:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fi:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Scatter Ratio\label{fi:region_scatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_scatter.tex}
				}
			}
			\caption{Average primary-total-backscatter rate regions.}
			\label{fi:region_config_1}
		\end{figure}

		% Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		For the specified scenario, Fig. \subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of UniScatter nodes, and the decrease of individual backscatter rate is unobvious.
		Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
		Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
		Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.

		\begin{figure}[!t]
			\centering
			\subfloat[Node Coverage\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Carrier Frequency\label{fi:region_frequency}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_frequency.tex}
				}
			}
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\caption{Average primary-total-backscatter rate regions.}
			\label{fi:region_config_2}
		\end{figure}

		Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
		When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
		Under the assumption of ideal backscatter decoding and re-encoding, Fig. \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
		However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
		When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
		In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
		Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
	\end{subsection}
	\label{se:simulation_results}
\end{section}

>>>>

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution for different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each UniScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}

	\begin{subsection}{Backscatter Rate versus Energy Discretization Bits}
		\begin{figure}[!t]
			\subfloat[Instance 1\label{fi:rate_bits_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/rate_bits_primary.tex}
				}
			}
			\subfloat[Instance 2\label{fi:rate_bits_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/rate_bits_backscatter.tex}
				}
			}
			\caption{Average achievable primary and total backscatter rates for different energy discretization bits.}
			\label{fi:rate_bits}
		\end{figure}
		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we now investigate the impact of threshold domain discretization on the total backscatter rate.

@@

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
				``BSP'' means backscatter symbol period.
			}
		\end{figure}
		The impacts of different input distribution, active beamforming, and decision threshold schemes on the average primary-backscatter rate region are explored in this study.

@@

	\begin{subsection}{Rate Region versus Configuration}
		\begin{figure}[!t]
			\centering
			\subfloat[Nodes\label{fi:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fi:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fi:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Coverage Radius\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
				``PSP'' means primary symbol period.
			}
			\label{fi:region_config}
		\end{figure}

		% % Fig. \ref{fi:region_config_1} reveals the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		% We present in \ref{fi:region_config_1} the impact of UniScatter nodes, input states, transmit antennas and scatter ratio on the achievable rate region.
		% For the specified scenario, Fig. \subref*{fi:region_tags} shows the total backscatter rate almost scales proportionally with the number of UniScatter nodes, and the decrease of individual backscatter rate is unobvious.
		% Besides, we conclude from \subref*{fi:region_states} that increasing the reflection states has a marginal effect on both primary and backscatter rates.
		% Those two facts motivates the use of numerous elementary/uncomplicated backscatter nodes, instead of high-order transponders or programmable high-resolution surfaces.
		% Figs. \subref*{fi:region_txs} and \subref*{fi:region_scatter} also prove increasing transmit antennas or scatter ratio can improve both primary and backscatter performance.

		% Fig. \subref*{fi:region_coverage} shows the tradeoff between coverage disk radius $r$ and achievable rate region.
		% When nodes are far from the user, both primary and backscatter rates decrease due to the product pass loss of forward and backward channels.
		% Under the assumption of ideal backscatter decoding and re-encoding, Fig. \subref*{fi:region_duration} suggests using lower symbol period ratio $N$ can boost total backscatter rate per primary symbol.
		% However, it requires more frequent detection and re-encoding at the user to maintain the primary rate.
		% When $N$ becomes sufficiently large, total backscatter rate approaches \num{0} and UniScatter nodes boil down to conventional \gls{ris} elements with fixed reflection pattern during whole channel block.
		% In Fig. \subref*{fi:region_frequency}, we observe that passive UniScatter nodes achieve higher backscatter rate at lower carrier frequency because of preferable propagation loss.
		% Finally, \subref*{fi:region_noise} prove the performance of energy detection is robust for a wide range of noise power.
	\end{subsection}
	\label{se:simulation_results}
\end{section}
